\documentclass[9pt]{extarticle}

\usepackage{Paper}

\fancyhead[L]{EE\_ECO}
\pdftitle{Life Cycle Assessment}
\setlength{\droptitle}{-2.5em}

% === TITLE ===
\title{\textbf{Life cycle assessment of different energy technologies \\ \Large Environmental Analysis \& Ecology}}
\author{Matteo Frongillo, Anastasia Linnik, Yannik Neukom}
\date{}

\geometry{
    a4paper,
    total={170mm, 257mm},   
    left=20mm,
    top=20mm,
    bottom=15mm
}

% === TEXT ===
\begin{document}
\maketitle
\thispagestyle{fancy}
\vspace{-2em}

\section{Photovoltaic Park {\small (Matteo)}}
\subsection{Paper 1}
\textbf{Title:} Estimating the environmental footprint of a grid-connected 20 MWp photovoltaic system\\
\textbf{Authors:} Artúr Szilágyi, Gyula Gróf\\
\textbf{Year:} 2020\\
\textbf{Journal/Source:} Solar Energy \parencite{SZILAGYI2020491}

The LCA in this paper is intended to support the planning and eco-design of photovoltaic
plants by estimating their environmental impact during the early planning phase. 
The goal of the paper is twofold: first, to assess the environmental impacts of the power
plant using the Product Environmental Footprint (PEF) methodology released by the Official
Journal of the European Union \parencite{EuropeanCommission2013Recommendation179} and second,
to compare the results of the simplified life-cycle model with those of the detailed model.

The study is comparative because it compares the simplified LCA with the detailed LCA, as
well as the PV power plant with the Hungarian grid mix.

The function of the system is to generate AC electricity and deliver it to the grid,
and the functional unit is 1kWh of AC electricity. The estimated lifetime of the plant
is of 25 years, and the expected lifetime production is 550 GWh.

The system boundary is cradle-to-grave, but with two model variants. The detailed model
applies a 99\% cut-off criterion, meaning that it aims to include more than 99\% of the
total materials and energy required for the construction of the power plant, and
includes PV modules, support structure, inverters, transformers,
cables, auxiliary infrastructure such as roads, fence and buildings, transport to site,
diesel and electricity for installation, packaging, site preparation, installation
waste, operation and maintenance (O\&M), replacement of faulty components,
and end-of-life transport and waste treatment. The excluded processes are capital
equipment and machinery life cycles, commuting, administration, marketing, R\&D, and the
energy needed for decommissioning, because it could not be reliably estimated.
The simplified model takes into account only the dominant contributors of the
environmental impact, which are PV panels, mounting structure, inverters, and cables.
Installation, transport and most O\&M processes are neglected; O\&M is reduced to
replacement of modules and inverters, and end-of-life is represented mainly by waste
cable treatment. This simplified boundary still captures most impacts.

\begin{figure}[H]
    \centering
    \resizebox{\textwidth}{!}{%
    \begin{tikzpicture}[
        font=\sffamily,
        phase/.style={
            draw=gray!35,
            fill=gray!18,
            rounded corners=12pt,
            line width=1.1pt,
            minimum width=5.25cm,
            minimum height=8.4cm,
            inner sep=0pt
        },
        title/.style={
            font=\bfseries\fontsize{15}{17}\selectfont,
            text=black!85
        },
        solidbox/.style={
            draw=black!85,
            fill=white,
            rounded corners=5pt,
            line width=1.1pt,
            minimum width=4.55cm,
            minimum height=0.72cm,
            align=center,
            inner xsep=6pt,
            inner ysep=6pt,
            font=\fontsize{13}{16}\selectfont
        },
        dashbox/.style={
            solidbox,
            dashed,
            dash pattern=on 5pt off 4pt
        }
    ]

    \node[phase] (prod) {};
    \node[phase, right=0.35cm of prod] (inst) {};
    \node[phase, right=0.35cm of inst] (oper) {};
    \node[phase, right=0.35cm of oper] (eol) {};

    \node[title, anchor=north] at ([yshift=-0.28cm]prod.north) {PRODUCTION};
    \node[title, anchor=north] at ([yshift=-0.28cm]inst.north) {INSTALLATION};
    \node[title, anchor=north] at ([yshift=-0.28cm]oper.north) {OPERATION};
    \node[title, anchor=north] at ([yshift=-0.28cm]eol.north) {END-OF-LIFE};

    \def\TopGap{1.15cm}
    \def\BoxGap{0.22cm}

    \node[solidbox, anchor=north] (p1) at ([yshift=-\TopGap]prod.north) {PV modules};
    \node[solidbox, anchor=north] (p2) at ([yshift=-\BoxGap]p1.south) {Supporting structure};
    \node[solidbox, anchor=north] (p3) at ([yshift=-\BoxGap]p2.south) {Transformers};
    \node[solidbox, anchor=north] (p4) at ([yshift=-\BoxGap]p3.south) {Cables};
    \node[dashbox, anchor=north] (p5) at ([yshift=-\BoxGap]p4.south) {Inverters};
    \node[dashbox, anchor=north, minimum height=1.35cm] (p6) at ([yshift=-\BoxGap]p5.south)
        {Materials for roads\\buildings, fence};

    \node[dashbox, anchor=north] (i1) at ([yshift=-\TopGap]inst.north) {Site preparation};
    \node[dashbox, anchor=north] (i2) at ([yshift=-\BoxGap]i1.south) {Energy carriers};
    \node[dashbox, anchor=north, minimum height=1.35cm] (i3) at ([yshift=-\BoxGap]i2.south)
        {Transport of\\components to site};
    \node[dashbox, anchor=north] (i4) at ([yshift=-\BoxGap]i3.south) {Wastes};
    \node[dashbox, anchor=north] (i5) at ([yshift=-\BoxGap]i4.south) {Packaging};
    \node[dashbox, fill opacity=0, text opacity=1, anchor=north] (i6) at ([yshift=-\BoxGap]i5.south)
        {\textit{Building machines}};

    \node[solidbox, anchor=north, minimum height=1.45cm] (o1) at ([yshift=-\TopGap]oper.north)
        {Replacement of PV\\modules, inverters};
    \node[dashbox, anchor=north] (o2) at ([yshift=-\BoxGap]o1.south) {Water for cleaning};
    \node[dashbox, anchor=north, minimum height=1.35cm] (o3) at ([yshift=-\BoxGap]o2.south)
        {Land use and herbi-\\cide application};
    \node[dashbox, anchor=north] (o4) at ([yshift=-\BoxGap]o3.south) {Transport for O\&M};
    \node[dashbox, fill opacity=0, text opacity=1, anchor=north] (o5) at ([yshift=-\BoxGap]o4.south)
        {\textit{Cleaning equipment}};

    \node[solidbox, anchor=north] (e1) at ([yshift=-\TopGap]eol.north) {Treatment of cables};
    \node[dashbox, anchor=north, minimum height=1.35cm] (e2) at ([yshift=-\BoxGap]e1.south)
        {Treatment of other\\wastes};
    \node[dashbox, anchor=north, minimum height=1.35cm] (e3) at ([yshift=-\BoxGap]e2.south)
        {Transport to\\treatment facility};
    \node[dashbox, fill opacity=0, text opacity=1, anchor=north, minimum height=2.05cm] (e4) at ([yshift=-\BoxGap]e3.south)
        {\textit{Energy and}\\\textit{machinery for}\\\textit{decommission}};

    \end{tikzpicture}%
    }
\caption{Life-cycle stages considered in the study. Processes with white background are considered in the detailed model, while processes with dashed borders are
excluded from the simplified model. Processes with italic font are excluded from both models.
}
\end{figure}

The inventory requires material quantities, component numbers, component masses,
transport distances, diesel and electricity use, replacement rates, degradation rate,
lifetime electricity generation and end-of-life treatment assumptions. Primary data is
retrieved by the commissioner of the power plants, while the secondary data, mainly
raw material, equipment, and fuels data, is taken from the latest available ecoinvent
database version (v3.5) released in 2018.
Most of the data is measured or calculated, while only transported quantity and
end-of-life assumptions are estimated. The case study is located in Felsőzsolca,
Hungary, and the data is representative of the Hungarian plant and European averages.
Regarding the precision and the completeness of the data, the secondary PV-module dataset
was checked against a review and found to be in the same range, but transport and
end-of-life data remain uncertain. The study did not model the decarbonisation of the
grid over the 25-year lifetime, limiting the comparison with the Hungarian grid mix.

The impact categories are grouped by damage type. Climate change is represented by
global warming 100a. Ecosystem quality includes freshwater and terrestrial
acidification, freshwater ecotoxicity, freshwater eutrophication, marine eutrophication,
and terrestrial eutrophication. Human health includes carcinogenic effects, ionising
radiation, non-carcinogenic effects, ozone layer depletion, photochemical ozone creation,
and respiratory effects from inorganics. Resources include fossil fuel depletion, land
use, minerals and metals depletion, and water depletion.

\begin{table}[H]
    \centering
    \renewcommand{\arraystretch}{1.25}
    \caption{Results of the case study vs. simplified model in PEF pts and impact coverage in (\%) by damage category}
    \begin{tabular}{l c c r}
        \textbf{Damage category} & \textbf{A: Simplified model} & \textbf{B: Detailed model} & \textbf{Share (A/B)} \\
        \hline
        Climate change & $8.67 \times 10^3$ PEF pt & $9.47 \times 10^3$ PEF pt & 92\% \\
        Ecosystem quality & $2.67 \times 10^4$ PEF pt & $2.95 \times 10^4$ PEF pt & 91\% \\
        Human health & $1.18 \times 10^5$ PEF pt & $1.36 \times 10^5$ PEF pt & 87\% \\
        Natural resources & $2.23 \times 10^5$ PEF pt & $2.38 \times 10^5$ PEF pt & 94\% \\
        \hline \hline
        Total & $3.76 \times 10^5$ PEF pt & $4.13 \times 10^5$ PEF pt & 91\%\\
    \end{tabular}
\end{table}
The total detailed result is equivalent to $7.5\times 10^{-4}$ PEF pt/kWh based on the
550 GWh lifetime output. The converted GWP is 6.57 g CO$_2$-eq/kWh for the detailed model
and 6.02 g CO$_2$-eq/kWh for the simplified model.

The main contributors are PV production at 47.0\% and steel structure at 24.3\%, followed
by the inverter production at 6.6\%, cable production at 5.5\%, and other smaller processes.
Thus, PV modules and the mounting structure dominate the footprint.

\subsection{Paper 2}
\textbf{Title:} Life Cycle Assessment of a ground-mounted 1778 kW$_\text{p}$ photovoltaic plant and comparison with traditional energy production systems\\
\textbf{Authors:} Umberto Desideri, Stefania Proietti, Francesco Zepparelli, Paolo Sdringola, Silvia Bini\\
\textbf{Year:} 2012\\
\textbf{Journal/Source:} Applied Energy \parencite{DESIDERI2012930}

\dots

\subsection{Comparison of Paper 1 and Paper 2}

\dots

\newpage
\section{Nuclear Power Plant {\small (Yannik)}}
\subsection{Paper 1}
\textbf{Title:} \\
\textbf{Authors:} \\
\textbf{Year:} \\
\textbf{Journal/Source:} 

\dots

\subsection{Paper 2}
\textbf{Title:} \\
\textbf{Authors:} \\
\textbf{Year:} \\
\textbf{Journal/Source:}

\dots

\subsection{Comparison of Paper 1 and Paper 2}

\dots

\newpage
\section{Coal-fired Power Plant {\small (Anastasia)}}
\subsection{Paper 1}
\textbf{Title:} \\
\textbf{Authors:} \\
\textbf{Year:} \\
\textbf{Journal/Source:} 

\dots

\subsection{Paper 2}
\textbf{Title:} \\
\textbf{Authors:} \\
\textbf{Year:} \\
\textbf{Journal/Source:} 

\dots

\subsection{Comparison of Paper 1 and Paper 2}

\dots
















\newpage
\appendix
\section{LCA Questionnaire}
\subsection{Goal and scope}
\subsubsection{Goal of LCA}
\begin{enumerate}
    \renewcommand{\labelenumi}{\alph{enumi})}
    \item What is the intended application of the LCA study?
    \item What is the purpose of the LCA study?
    \item Who is the intended audience of the LCA report?
    \item Is the LCA study based on a comparative analysis?
\end{enumerate}

\subsubsection{Scope of LCA}
\begin{enumerate}
    \renewcommand{\labelenumi}{\alph{enumi})}
    \setcounter{enumi}{4}
    \item What is the function(s) of the product and which functional unit has been applied?
    \item Plan and describe the system boundaries of the LCAs using a process flow diagram showing the processes, their relationships, and the function of the system.
    \item What data and type of data are needed to calculate inventory results
    and selected impact assessment categories?
    \begin{itemize}[label=--]
        \item Data quality requirements, assumptions and limitations
        \item Data acquisition: Is the data measured, calculated or estimated? How much of the data required is primary data (in \%) and how much data is taken from literature and databases (secondary data)?
        \item Time-reference: When was the data obtained and have there been any major changes since the data collection that might affect the results?
        \item Geographical reference: For what country or region is this data relevant?
        \item Is the secondary data from literature or databases representative for state-of-the-art-technology or for older technology?
        \item Precision: Is the data a precise representation of the system?
        \item Completeness: Are any data missing? How are data gaps filled?
        \item Representativeness, consistency, reproducibility: Is the data representative, consistent and can it be reproduced?
    \end{itemize}
    \item What impact categories are used?
\end{enumerate}

\subsection{Results of Life Cycle Impact Assessment (LCIA)}
\begin{enumerate}
    \renewcommand{\labelenumi}{\alph{enumi})}
    \item State the results of the different impact categories in numbers.
    \item Interpret the two case studies by considering the following:\\
        Results are checked and evaluated to check if they are consistent with the goal and scope definition. This includes: identification of significant issues
        (e.g. inventory elements or impact categories missing) and evaluation/interpretation of results (e.g. comparability)
\end{enumerate}

\newpage
\section{References}
\begingroup
\sloppy
\setlength{\emergencystretch}{3em}
\printbibliography
\par
\endgroup



\end{document}
